---
title: "Reflection"
author: "Jiatao Wang"
date: "11/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data Scientist

Data scientist is a trending job/role that involves combination of the skill sets. Coding skills, knowledge of statistics, mathematics and machine learning. Even though the job specifications vary for companies, those skills is undeniably necessary to be a successful data scientist. With the in-depth exploration of what a data scientist could do in this course, I think we can gain more pleasure if we apply our skill sets to real world situations and dive into the data science world. Because data science is eventually the tool to help us understand and interpret our lives better and make our life easier. 

## Using R 

R is a really convenient programming tool. It performs good statistical analysis, data cleaning and data visualization with simple coding. There are unlimited explorations for me in R. Take R shiny as an example. R shiny contains tons of options that you can play around with. I will continue to use R going forward since R has become a bridge for me to connect my area of interest with my skill sets. 

## More Discussion

It is exciting and intriguing to learn API and R shiny in this course. They are good tools for us to share information and interact with others. I could now explore more on statistics of game and anime based on my knowledge of data science. 

Thank you ST558! Thank you Professor Justin! 

```{r , include=TRUE, eval=FALSE}
rmarkdown::render("/Users/CKA/Documents/CKA/reflection/_Rmd/2021-11-23-Reflection-Blog-Post.Rmd",
              output_format = "github_document", 
              output_dir = "/Users/CKA/Documents/CKA/reflection/_posts",
              keep_html = FALSE
                
              )

```

