---
title: "Programming Background"
author: "Jiatao Wang"
date: "9/3/2021"
---

## Response
I think R is a pretty handy and powerful programming language. It could manipulate data set using simple functions and those functions are pretty easy to understand and to be remembered. I have used SAS Python and SQL, putting SQL away, I think SAS have a more sophisticated procedure to read data and do the data cleaning method, especially for the unstructured data set. But SAS is more powerful for doing statistical analysis, the outputs produced by SAS have more interpretability. Python, a more object oriented language, also have lots of advantage, more easier to access API etc. I think R is not a difficult language to learn as long as you have some programming background before. I learned R prior to this course and I think there are lots of functions in R really powerful and convenient for us to use. Such as some machine learning techniques and statistical modeling. But sometimes R is pretty slow comparing to Python.  

## R Markdown Output

```{r, include=TRUE,echo=TRUE,eval = TRUE}
knitr::opts_chunk$set(fig.path = "../images/")
plot(iris3)
```


```{r , eval = FALSE, include = FALSE}
library(rmarkdown)
rmarkdown::render("/Users/CKA/Documents/CKA/st558/_Rmd/st558-09-07-2021-Second Post Blog.Rmd", 
              output_format = "github_document", 
              output_dir = "/Users/CKA/Documents/CKA/st558/_posts",
              output_options = list(
                html_preview = FALSE
                )
              )
```